\cvsection{Presentations}
\begin{cventries}
  \cventry
    {Full Stack Development w/ Meteor}
    {CPOSC 2015}
    {Lancaster, Pa}
    {Oct. 2015}
    {
      \begin{cvitems}
        \item {\textbf{Writing a real-time comment system in meteor}: A brief presentation explaining the power of meteor followed by a 20min live demonstration of building a full featured commenting system including user management and live comment updates during the talk.}
        \item {\href{http://rjfisher.github.io/CPOSC-2015-Meteor-Slides/}{\faGithubSquare\ Slides Online}}
      \end{cvitems}
    }

  \cventry
    {ESRI Online: Powerful Cloud Based GIS}
    {Tech Lancaster}
    {Lancaster, Pa}
    {Jun. 2015}
    {
      \begin{cvitems}
        \item {\textbf{A brief overview of ESRI Online}: The advantages of using this cloud based GIS system for data management, data editing, and software development.  Showed a quick example of how to use ESRI Online to create powerful, fully featured mapping applications for the web.  Then using the same data for native applications using the ERSI mobile application APIs.}
        \item {\href{http://rjfisher.github.io/TechLancaster-ESRI-Online/}{\faGithubSquare\ Slides Online}}
      \end{cvitems}
    }

  \cventry
    {meteorjs: A Reactive Web Framework}
    {Tech Lancaster}
    {Lancaster, Pa}
    {Dec. 2014}
    {
      \begin{cvitems}
        \item {\textbf{A brief overview of meteor}: The advantages of using this real-time JavaScript platform for development and the power of automatic client/server synchronization.}
        \item {\href{https://github.com/rjfisher/TechLancaster-Meteor-Talk/}{\faGithubSquare\ Slide Code Online}}
      \end{cvitems}
    }

  \cventry
    {Presenter for Merits of Mobile GIS}
    {(IMAGIN): Geospatial Workshop series}
    {University of Michigan}
    {Feb. 2012}
    {
      \begin{cvitems}
        \item {\textbf{Morning Session Presentation}: An overview of the power and options for mobile GIS solutions.  Looked at the pros/cons of a mobile friendly website, native application, and hybrid applications.}
        \item {\textbf{Afternoon Session Presentation}: An overview of a specific case study.  Using the City of Philadelphia's SWEEP Mobile ticketing system to show the power of using mobile technology with GIS systems to provide impressive returns of investment.}
      \end{cvitems}
    }
\end{cventries}
